\subsection{A* Search Algorithm}
\subsubsection*{Concepts}
\begin{itemize}
    \item \textbf{Introduction:} A* Search is a graph search algorithm that combines the advantages of both Dijkstra's algorithm and greedy best-first search. It uses both the actual cost from the start node (g-value) and an estimated cost to the goal node (h-value) to guide the search.
    \item \textbf{Traversal Method:} A* Search uses a priority queue ordered by the sum of g-value and h-value (f-value) to expand nodes with the lowest estimated total cost first.
\end{itemize}
\subsubsection{Heuristic function note}
I code 2 version of Astar algorithm, one with the heuristic function as the Euclidean distance, and the other with the heuristic function as the Manhattan distance. 

The Euclidean distance is calculated as follows:
\[h(node) = \sqrt{(goal_x - node_x)^2 + (goal_y - node_y)^2}\]
The Manhattan distance is calculated as follows:
\[h(node) = |goal_x - node_x| + |goal_y - node_y|\]
\subsubsection*{Pseudo Code}
function BEST-FIRST-SEARCH(problem, f) was mentioned in Section \ref{UCS_best_first_search}.
\begin{verbatim}
function A-STAR-SEARCH(problem) returns a solution node or failure
    return BEST-FIRST-SEARCH(problem, g+h)
\end{verbatim}

\subsubsection*{Complexity}
\begin{itemize}
    \item \textbf{Time Complexity:} In the worst case, A* Search has a time complexity of \( O(b^d) \), where \( b \) is the branching factor of the graph and \( d \) is the depth of the optimal solution. However, with a good heuristic function, it often performs much better.
    \item \textbf{Space Complexity:} A* Search has a space complexity of \( O(|V|) \), where \( V \) is the number of vertices, due to the priority queue and the visited set.
\end{itemize}

\subsubsection*{Properties}
\begin{itemize}
    \item \textbf{Completeness:} A* Search is complete if a solution exists, given that the branching factor is finite and all edge costs are non-negative.
    \item \textbf{Optimality:} A* Search is optimal if the heuristic function \( h(s) \) is admissible (never overestimates the true cost to reach the goal) and consistent (satisfies the triangle inequality).
    \item \textbf{Traversal Type:} A* Search explores nodes based on the f-value, which combines the g-value (cost from start to current node) and the h-value (estimated cost from current node to goal).
\end{itemize}