\subsection{Iterative Deepening Search (IDS) Algorithm}
\subsubsection*{Concepts}
\begin{itemize}
    \item \textbf{Introduction:} Iterative Deepening Search (IDS) combines the benefits of depth-first and breadth-first search. It performs a series of depth-limited searches, increasing the depth limit with each iteration.
    \item \textbf{Traversal Method:} IDS uses a depth-limited search repeatedly, increasing the limit after each complete pass until a solution is found or the search space is exhausted.
\end{itemize}

\subsubsection*{Pseudo Code}
\begin{verbatim}
function ITERATIVE-DEEPENING-SEARCH(problem) returns a solution node or failure
    for depth = 0 to oo do
        result←DEPTH-LIMITED-SEARCH(problem, depth)
        if result != cutoff then return result

function DEPTH-LIMITED-SEARCH(problem, l) returns a node or failure or cutoff
    frontier←a LIFO queue (stack) with NODE(problem.INITIAL) as an element
    result←failure
    while not IS-EMPTY(frontier) do
        node←POP(frontier)
        if problem.IS-GOAL(node.STATE) then return node
        if DEPTH(node) > l then
            result←cutoff
        else if not IS-CYCLE(node) do
            for each child in EXPAND(problem, node) do
                add child to frontier
    return result
\end{verbatim}

\subsubsection*{Complexity}
\begin{itemize}
    \item \textbf{Time Complexity:} \(O(b^d)\), where \(b\) is the branching factor and \(d\) is the depth of the shallowest goal node. This is because IDS performs multiple passes, but the time complexity remains exponential.
    \item \textbf{Space Complexity:} \(O(bd)\), as IDS only needs to store a stack of nodes up to the current depth limit.
\end{itemize}

\subsubsection*{Properties}
\begin{itemize}
    \item \textbf{Completeness:} IDS is complete if the branching factor is finite, meaning it will eventually find a solution if one exists.
    \item \textbf{Optimality:} IDS is optimal if all step costs are equal, as it finds the shallowest goal node.
    \item \textbf{Traversal Type:} IDS performs iterative deepening, combining depth-first search's space efficiency with breadth-first search's completeness.
\end{itemize}
